Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-02-23 apples_and_oranges.qmd
Trying to debug error with the percent_women variable, will revisit on Monday

```{r, warning=FALSE, message = FALSE, echo=FALSE}
###########Libraries needed
library(tidyverse)
library(truncnorm)
library(metafor)
```

@@

# Step 2: turn dataframes to long
# A: turn long the rows with active
active_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, active_type, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active,
                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active) %>% 
  rename(treatment = descr_active) %>% 
  rename(type = active_type) %>% 
  rename_with(~ str_remove(., "_active")) %>% 
  mutate(arm_effect_size = "cohens_d_active") %>% # chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

control_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, control_type, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control,
                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control) %>% 
  rename(treatment = descr_control) %>% 
  rename(type = control_type) %>% 
  rename_with(~ str_remove(., "_control")) %>% 
  mutate(arm_effect_size = "cohens_d_control") %>% #chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

@@

>>>>

```{r, warning=FALSE, message = FALSE, echo=FALSE}
###########Libraries needed
library(tidyverse)
library(truncnorm)
library(metafor)
library(meta)
```

@@

# Step 2: turn dataframes to long
# A: turn long the rows with active
active_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, active_type, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active,
                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active, percent_women, percent_women_std_error, mean_age, sd_age) %>% 
  rename(treatment = descr_active) %>% 
  rename(type = active_type) %>% 
  rename_with(~ str_remove(., "_active")) %>% 
  mutate(arm_effect_size = "cohens_d_active") %>% # chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

control_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, control_type, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control,
                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control, percent_women, percent_women_std_error, mean_age, sd_age) %>% 
  rename(treatment = descr_control) %>% 
  rename(type = control_type) %>% 
  rename_with(~ str_remove(., "_control")) %>% 
  mutate(arm_effect_size = "cohens_d_control") %>% #chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

@@

# Now we want to do look at baseline severity when we exclude psy studies with sub clinical depression levels

# We will do in two ways
# First by excluding studies with a diagnostic classification of "sub"

clin_study_ids <-
  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id

clin_studies_baseline_metareg <- all_studies_baseline_metareg %>%
  filter(new_study_id %in% clin_study_ids)

#turn sds to sec
clin_studies_baseline_metareg$baseline_stand_error <- clin_studies_baseline_metareg$perc_baseline_sd/
                                        sqrt(clin_studies_baseline_metareg$baseline_n)

model_1 <- as.formula(~ four_level_var)
condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
                                                              #throughout
# also change this for the function to work
clin_studies_baseline_metareg$baseline_mean <- clin_studies_baseline_metareg$perc_baseline_mean
results_clin_studies_baseline_metareg <- run_metareg_and_extract(clin_studies_baseline_metareg,  
                                                         model_1, condition)

# Now lets include only studies with classification of "mdd"

mdd_study_ids <-
  df_appl_v_orange[df_appl_v_orange$diagnosis == "mdd",]$new_study_id

mdd_studies_baseline_metareg <- all_studies_baseline_metareg %>%
  filter(new_study_id %in% mdd_study_ids)

mdd_studies_baseline_metareg %>% 
  filter(four_level_var %in% c("psychotherapy_active","psychotherapy_control")) %>%
  summarise(n = n())

#turn sds to sec
mdd_studies_baseline_metareg$baseline_stand_error <- mdd_studies_baseline_metareg$perc_baseline_sd/
                                        sqrt(mdd_studies_baseline_metareg$baseline_n)

model_1 <- as.formula(~ four_level_var)
condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
                                                              #throughout
# also change this for the function to work
mdd_studies_baseline_metareg$baseline_mean <- mdd_studies_baseline_metareg$perc_baseline_mean
results_mdd_studies_baseline_metareg <- run_metareg_and_extract(mdd_studies_baseline_metareg,  
                                                         model_1, condition)

# # Now CBT studies
# 
# cbt_study_ids <-
#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt",]$new_study_id
# 
# cbt_studies_baseline_metareg <- all_studies_baseline_metareg %>%
#   filter(new_study_id %in% cbt_study_ids) %>% 
#   filter(!(arm_effect_size == "cohens_d_active" & !(type == "cbt")))
# 
# 
# #turn sds to sec
# cbt_studies_baseline_metareg$baseline_stand_error <- cbt_studies_baseline_metareg$perc_baseline_sd/
#                                         sqrt(cbt_studies_baseline_metareg$baseline_n)
# 
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# # also change this for the function to work
# cbt_studies_baseline_metareg$baseline_mean <- cbt_studies_baseline_metareg$perc_baseline_mean
# results_cbt_studies_baseline_metareg <- run_metareg_and_extract(cbt_studies_baseline_metareg,  
#                                                          model_1, condition)

# Now CBT + all med studies

cbt_meds_study_ids <-
  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0, ]$new_study_id

cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
  filter(new_study_id %in% cbt_meds_study_ids) %>% 
  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))

#turn sds to sec
cbt_meds_studies_baseline_metareg$baseline_stand_error <- cbt_meds_studies_baseline_metareg$perc_baseline_sd/
                                        sqrt(cbt_meds_studies_baseline_metareg$baseline_n)

model_1 <- as.formula(~ four_level_var)
condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
                                                              #throughout
# also change this for the function to work
cbt_meds_studies_baseline_metareg$baseline_mean <- cbt_meds_studies_baseline_metareg$perc_baseline_mean
results_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(cbt_meds_studies_baseline_metareg,  
                                                         model_1, condition)

# Look at the diagnostics of included studies

filtered_data <- df_appl_v_orange %>%
  filter(psy_or_med == 1) %>% 
  filter(new_study_id %in% cbt_meds_study_ids) %>%
  distinct(new_study_id, .keep_all = TRUE)

summary_result <- filtered_data %>%
  group_by(diagnosis) %>%
  summarise(count = n())

# Now the CBT + med studies, filtering out the subclinical studies

# Now CBT + all med studies

clin_cbt_meds_study_ids <-
  df_appl_v_orange[(df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0) & df_appl_v_orange$diagnosis != "sub", ]$new_study_id

clin_cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
  filter(new_study_id %in% clin_cbt_meds_study_ids) %>% 
  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))

#turn sds to sec
clin_cbt_meds_studies_baseline_metareg$baseline_stand_error <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_sd/
                                        sqrt(clin_cbt_meds_studies_baseline_metareg$baseline_n)

model_1 <- as.formula(~ four_level_var)
condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
                                                              #throughout
# also change this for the function to work
clin_cbt_meds_studies_baseline_metareg$baseline_mean <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_mean
results_clin_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(clin_cbt_meds_studies_baseline_metareg,  
                                                         model_1, condition)

# Now start looking at perc_women variable

met_perc_women <- metagen(TE = "percent_women",
                           seTE = "percent_women_std_error",
                           studlab = "new_study_id",
                          data = df_long_for_metan,
                           sm = "SMD",
                           fixed = FALSE,
                           random = TRUE,
                           method.tau = "REML",
                           hakn = TRUE,
                           title = "percentage women across studies",
                          subgroup = "four_level_var",
                          tau.common = FALSE,
                          na.rm = TRUE)

# ### get CDRS clin studies
#  clin_cdrs_studies_baseline_metareg <- cdrs_studies_for_baseline_metareg %>% 
#    filter(new_study_id %in% clin_study_ids)
#  
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# 
# results_clin_cdrs_metareg_baseline <- run_metareg_and_extract(clin_cdrs_studies_baseline_metareg,  
#                                                          model_1, condition)
# 
# # Just realised this is identical, as all the studies that use the CDRS have clinical samples. 
# 
# ### get HAM-D clin studies
#  clin_hamd_studies_for_baseline_metareg <- hamd_studies_for_baseline_metareg %>% 
#    filter(new_study_id %in% clin_study_ids)
# 
# 
# model_1 <- as.formula(~ four_level_var)
# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
#                                                               #throughout
# results_clin_hamd_studies_for_baseline_metareg <- run_metareg_and_extract(clin_hamd_studies_for_baseline_metareg, 
#                                                          model_1, condition)
# 
# results_clin_hamd_studies_for_baseline_metareg$condition <-  levels(list_df_simulated[[1]]$four_level_var)
# 
#
